---
title: "R Notebook"
output: html_notebook
---

##Data Preperataion

```{r fetchdata, include=TRUE,echo=FALSE}
cwd <- paste0(getwd())
setwd(cwd)

download.file(url = "https://s3.amazonaws.com/istreet-assets/i0jhsz_Udi_Zl2jxJ-c-pQ/CMS_OPEN_PAYMENTS_DEC_2013.zip"
              ,destfile = "CMS_OPEN_PAYMENTS_DEC_2013.zip")
cmszip <- unzip("CMS_OPEN_PAYMENTS_DEC_2013.zip")
cmspayments <- read.csv(cmszip)

```


### Data Exploration
1.	Who are the top 10 companies making payments?  For the top five companies, what therapeutic areas are they investing in? 
Create data visualizations to compare and contrast these five companies and highlight any potential insights and tell a story based on what you see. 
(For the purposes of this question, assume that “Physician_Specialty” is equivalent to therapeutic area.) 


```{r dataexploration, echo=TRUE,include=TRUE}
#names(cmspayments)
#Companies is "Submitting_Applicable_Manufacturer_or_Applicable_GPO_Name"
toppayor <- aggregate(Total_Amount_of_Payment_USDollars ~ Submitting_Applicable_Manufacturer_or_Applicable_GPO_Name
                                                        + Physician_Specialty
                      ,cmspayments,FUN = sum)
colnames(toppayor) <- c("Company","TotalPayment")


```